Verifying Spatial Properties of Array Computations

### 2017-04-13 oopsla17/oopsla17.tex
including more of the model

\usepackage{stencilmacros}

@@

% For evluation and empirical study
% Defines the commands (headers)
\input{resultsCmds}
% renews the commands with actual data
% \input{results}

@@

\begin{defn}[Index scheme]
  An $N$-dimensional \emph{index scheme} is a vector of length $N$ of
  extended integer sets, \ie{}, a member of $\mathcal{P}(\bz)^{N}$.
  An alternate (equivalent) view is of a $N$-times finite Cartesian
  product on subsets of $\bz$.  We use $S, T, U$ to denote index
  schemes.

@@

%\begin{theorem}
%$N$-dimensional index schemes form a lattice where join and m
%\end{theorem}

@@

\begin{restatable}{lem}{vectorUnion}
\label{lem:vector-union}
Let $S, T$ be $N$-dimensional index schemes such that
$\pi_i(S) = \pi_i(T)$ for all $1 \leq i \leq N$ apart 
from some dimension $k$ where $\pi_k(S) \neq \pi_k(T)$,
then:
%
  \begin{equation*}
    S \; \cup \; T
    =
    \pi_1(S) \times \cdots \times
    (\pi_k(S) \cup \pi_k(T)) \times \cdots \times
    \pi_N(S)
  \end{equation*}
%
\end{restatable}
%

\begin{defn}
  We define an extended notion of closed interval on $\bz{}$ which may contain
  a \emph{hole} at the origin, written \interv{a}{b}{c} where $a$ and $b$ are
  drawn from \bz{} with $a \leq 0 \leq b$
   and $c$ is drawn from $\mathbb{B} = \{ \mathsf{true}, \mathsf{false}
  \}$. Intervals are interpreted as sets as follows:
%
  \begin{equation*}
    \interv{a}{b}{c} \triangleq
      \{ n \mid a \leq n \leq b \wedge (\neg c \implies n \neq 0) \}
  \end{equation*}
%
  We denote the set of all such intervals (sets) as
   $\textit{Interval}$. If the superscript is
  omitted it is treated as $\mathsf{true}$.
\end{defn}

@@

\begin{defn}{(\emph{Interval subspace})}
  An interval subspace is a finite Cartesian product of intervals on
  \bz{} or \bz itself, 
  denoted by the set $\textit{Interval}^N$ for a product of $N$ intervals.
\end{defn}

>>>>

\errorcontextlines 10000
\usepackage{stencilmacros}

@@

% For evluation and empirical study
% Defines the commands (headers)
\input{resultsCmds}
\input{studyResults}
% renews the commands with actual data
% \input{results}

@@

\begin{defn}[Index scheme]
  An $N$-dimensional \emph{index scheme} is a vector of length $N$ of
  extended integer sets, \ie{}, a member of $\mathcal{P}(\bz)^{N}$.
  An equivalent view of these vectors is as an $N$-times finite Cartesian
  product on subsets of $\bz$.  We use $S, T, U$ to denote index
  schemes.

@@

@@

\begin{restatable}{lem}{vectorUnion}
\label{lem:vector-union}
Let $S, T$ be $N$-dimensional index schemes such that
$\pi_i(S) = \pi_i(T)$ for all $1 \leq i \leq N$ apart 
from some dimension $k$ where $\pi_k(S) \neq \pi_k(T)$,
then:
%
  \begin{equation*}
    S \cup  T
    =
    \pi_1(S) \times \cdots \times
    (\pi_k(S) \cup \pi_k(T)) \times \cdots \times
    \pi_N(S)
  \end{equation*}
%  \begin{equation*}
%    S \cup T
%    =
%    (\prod_{i=1}^{k-1} \pi_i(S)) \times (\pi_k(S) \cup \pi_k(T)) \times \prod_{k+1}^{N} \pi_i(S)
%  \end{equation*}
%
\end{restatable}
%

\begin{defn}[Intervals with an optional hole]
  We define an extended notion of closed interval on $\bz{}$ which may contain
  a \emph{hole} at the origin, written \interv{a}{b}{c} where $a$ and $b$ are
  drawn from \bz{} with $a \leq 0 \leq b$
   and $c$ is drawn from $\mathbb{B} = \{ \mathsf{true}, \mathsf{false}
  \}$. Intervals are interpreted as sets as follows:
%
  \begin{equation*}
    \interv{a}{b}{c} \triangleq
      \{ n \mid a \leq n \leq b \wedge (\neg c \implies n \neq 0) \}
  \end{equation*}
%
  We denote the set of all such intervals (sets) as
   $\textit{Interval}$. If the superscript is
  omitted it is treated as $\mathsf{true}$.
\end{defn}

@@

We define two subsets of index scheme: \emph{subscript} schemes and
\emph{interval} schemes:

\begin{defn}[Interval scheme]
  An interval scheme is a finite Cartesian product of intervals on
  \bz{} or \bz{} itself, 
  denoted by the set $\textit{Interval}^N$ for a product of $N$ intervals.
\end{defn}

\begin{defn}[Subscript scheme]
  A $N$-dimensional \emph{subscript scheme} is an $N$-dimensional
  interval scheme where:
  %
  \begin{equation*}
    \forall i.\ 1 \leq i \leq N \implies
      \pi_i (S) = [p, p] 
      \; \vee \;
      \pi_i (S) = \bz{}
    \end{equation*}
    That is, the $i^{th}$ component of the set is either a singleton
  in $\mathbb{Z}$ or the infinite interval.
\end{defn}
%
\dnote{May want a predicate as well}

\begin{defn}{(\emph{Region})}
  A region \region{N} is an $N$-dimensional index scheme
  (\ie{}, $\region{N} \subseteq \mathcal{P}(\bz)^N)$ defined as the smallest set satisfying the following:
%
  \begin{enumerate}
    \item If $R$ is in $\textit{Interval}^N$, then $R$ is in \region{N}.
    \item If $R$ and $S$ are in \region{N}, then so are $R \cap S$ and
      $R \cup S$.
  \end{enumerate}
\end{defn}

\begin{prop}{}
  $(\region{N},\subseteq)$ is a distributive lattice.
\end{prop}
%
\begin{proof}(sketch)
%  Any sublattice of a distributive lattice is a distributive lattice. Power sets
%  partially ordered with subset relation are distributive lattices. \region{N}
%  is a subset of $\mathcal{P}{(\bz{})^N}$ since all interval schemes are
%  subsets of this power set and; union and intersection cannot add an element
%  that is not already in the powerset. The inductive definition ensures that
%  \region{N} is closed under these operations. Therefore, \region{N} is a
%  distributive sublattice of $(\mathcal{P}{(\bz{})^N}, \subseteq)$.
\end{proof}
